Delay Comparison of Different Switch Architectures

### 2013-11-10 MSReport/MSThesis.tex
explanation of code in begun.

 The simulations fell into two categories: an open loop version meant to measure switch throughput, and a closed loop version meant to mimic TCP operation over the switch.  %We go into more depth in subsequent sections.

@@

The TCP window size is updated by additive increase multiplicative decrease, with feedback coming in the form of acks that are generated whenever a packet successfully traverses the switch.  The acks in our simulation are not actually packets sent through our network, but rather simply notify our TCP simulator after an artificially determined delay.  After an ack notifies the TCP flow it adjusts its send window statistics accordingly.  The ack is delayed by a factor of 10 times the delay it took the packet to traverse the switch in order to simulate the round trip time in a datacenter that has five switches between the input and its intended output.\\

@@

\begin{itemize}
\item all to all 
\item spread and aggregate 
%\item three simultaneous spread and aggregate
\item typical 
\item typical and spread and aggregate \\
\end{itemize}

@@

>>>>

 The simulations fell into two categories: an open loop version meant to measure switch throughput, and a closed loop version meant to mimic TCP operation over the switch.  For more details on the simulator design please see appendix \ref{code_design}.%We go into more depth in subsequent sections.

@@

The TCP window size is updated by additive increase multiplicative decrease, with feedback coming in the form of acks that are generated whenever a packet successfully traverses the switch.  The acks in our simulation are not actually packets sent through our network, but rather simply notify our TCP simulator after an artificially determined delay.  After an ack notifies the TCP flow it adjusts its send window statistics accordingly.  The ack is delayed by a factor of 10 times the delay it took the packet to traverse the switch in order to simulate the round trip time in a datacenter that has five switches between the input and its intended output.

@@

\begin{itemize}
\item all to all 
\item spread and aggregate 
%\item three simultaneous spread and aggregate
\item typical 
\item typical and spread and aggregate
\end{itemize}

@@

 %\appendix
  \appendices 
 \section{Simulation Design} \label{code_design}

 Because the simulation tracked events on two very different time scales (that of packet transmissions and that of schedulers clock ticks) we chose to use an event driven simulator.  This means that we had a mechanism for calculating the next event (and time at which it occurred) given the current state of the system, instead of calculating the new state at each time step.

 \subsection{Main components}
 To accommodate this simulation model, the heart of the code was split into essentially two logical pieces: State variables, and state transitions.  Logically, the heart of the simulator looks like this:
 \begin{verbatim}
 while(num_events<tot_num_events)
 {
      event = next_event()
      update_state(event)
      num_events=num_events+1
 }
 \end{verbatim}
 The update$\_$state() function, takes a state transition (in the form of an instantiation of the Event class) and calculates the new state of the system.  Similarly, the next$\_$event() function calculates the next state transition based on the current state of the system.  Of course there are sanity checks built in, machinery to setup the initial state, and machinery used to record the results of the calculation, but at the most basal level, this is what the simulator is doing.  To understand this function I will talk briefly about what constitutes the state, what an event is, and how the next event is calculated.

 \subsubsection{State}

The state with a few minor exceptions mainly of different queues of packets which contain the crucial information about where to route the packets and when they arrived into the system.  Generally each state is regulated by a particular kind of event.
\begin{itemize}
\item {\bf Current Time}\\
 --  This variable determined the time elapsed in scheduler clock ticks since the start of the simulation.
\item {\bf Packet Generation State}\\
 --  For the simulations which generated packets as Markov chains as inputs each flow had an associated state (ON or OFF)
\item {\bf Flow Queues}\\
 --  Upon generation each packets are placed in flow queues, which represent queues of different application flows within a computer.  Depending on the simulation, packets would stay in here until released by the TCP flow regulator.
\item {\bf NIC state}\\
 --  This state keeps track of which flows are being transferred from the ``computer" and transferred to the network.  In the closed loop simulations this is regulated by the TCP state.
\item {\bf Switch Queues}\\
--  Once a packet is transferred out of the flow queues, it is placed into the switch queues, which in conjunction with the crossbar state is used to calculate the next scheduler events.
\item {\bf Crossbar State}\\
--  The crossbar state keeps track of which inputs and outputs are currently transmitting packets and how much longer it will take to finish the transmission.
\item {\bf Event Heap (ACKs)}\\
--  Upon exit of the system, and ACK along with an appropriate arrival time is generated and placed onto the event heap.  
\end{itemize}

\subsection{Auxiliary structures}
